Occurance rate of galaxy pairs across cosmic time:\\ Local Group analogs in a cosmological context

### 2024-01-04 paper/apj_sub/resubmission-Dec2023/response.txt

We thank the reviewer for the thorough, thoughtful comments on our manuscript, which prompted us to reexamine the language used to discuss observations throughout the paper.

All additions/edits to the paper are marked in bold red text (with the \add{} command).

Please find a more detailed description of each of the changes below, as well as responses to individual comments in the order that they appeared. Also, please note that we have added an additional coauthor, Nitya Kallivayalil, who was mistakenly not included in the author list during the first submission.

Best,
Katie

Begin reviewer comments:
------------------------

The manuscript entitled " A physically motivated framework for measuring the mass and redshift dependence of galaxy pair fractions across cosmic time" by Chamberlain et al. contributes to the analysis of galaxy growth via mergers using numerical simulations to determine the fraction of close pairs and its dependence on mass and redshift. The separation with respect to stellar mass is especially interesting as the differences in the pair fraction predicted by the simulations could be tested with deep survey data (at least out to intermediate redshifts).

On a practical note, I find that the "dynamic" definition of the pair separation with respect to the virial radius of the host halo would be rather complicated to implement in observational data, as the way this virial radius is selected (from the unobservable DM) would unavoidably introduce systematics that would induce artificial trends hard to disentangle. This will be especially harder if photometric redshifts are used (note that this type of study requires a large number of sources with a high completeness down to relatively small apparent distances, something that many spectroscopic surveys struggle with). While less optimal, a fixed separation criterion allows for a robust selection in both simulations and observations. Perhaps this is the reason why this paper lacks a comprehensive comparison with observational data.
–
>> We thank the reviewer for this comment. In this study we have selected pairs using a standard pair separation cut, as is done in observations (<50 kpc, 100 kpc, 150 kpc, etc). We illustrated that such a fixed separation will result in completeness issues, which will limit the effectiveness of comparison against simulations. This will be particularly true for efforts to tease out physical differences in the pair fractions of massive vs low mass galaxies over time.

To address this shortcoming, we have introduced a “dynamic” definition that involves the virial radius of the host.  The referee is correct that this is a well defined quantity in the simulations, but not in the observations. However we disagree that such an approach is unfeasible for observational studies. A dynamic definition can be introduced in an observational study using the halo-to-stellar mass relation (abundance matching). This is the same relationship we have used in our theoretical study to infer stellar masses from halo mass. As such, the errors introduced would be similar to those of the theoretical study. No comparison between theory and observations is devoid of assumptions. Applying a “dynamic” definition for pair separation is simply an example method where the introduced errors would be similar for both theory and observational samples. 
–

There is also a concern I have regarding the sample selection. On page 2, col 2, line 132, the authors state that "... no other more massive perturbers are nearby", admittedly with the intention of focusing on the pairs and somehow removing the effect of the environment over larger scales. However, this will cause a systematic in the selection towards isolated pairs. In general, the distribution of pairs will be heavily dependent on the environment. 
–
>>We thank the reviewer for their response, and have clarified in the draft that these results are true of isolated environments only.

In this study, our primary goal is to identify whether physical differences between the fraction of low mass galaxy pairs and high mass galaxy pairs exist as a function of time. We recognize that an isolation criteria can be challenging to implement in observations at high z. However, an isolation criterion is necessary in our study to remove environmental factors that can impact pair counts, such as the disruption of pairs by a more massive host. This isolation criteria enables the low mass and high mass pairs to be compared directly, as lower mass pairs are more susceptible to environmental effects. Furthermore, isolation criteria are standardly applied in studies of galaxies at low z (see Geha+ 2012, which studies isolated quenched vs. star forming galaxies at 1.5Mpc from other galaxies, or Besla+ 2018 which applies isolation criteria to the SDSS sample in their paper). We have added language to make it clear that requiring isolation may be challenging at high z. 
–

The imposed selection will target close pairs in lower density regions, affecting in several ways the analysis:

1) Observational samples need estimates of the stellar mass of the galaxies, which requires a derivation of the stellar M/L, itself dependent on the star formation history of the galaxies. A sample targeting isolated galaxies may produce different M/L than a more standard field distribution, on samples defined in groups/clusters. This is even more relevant when a large range of cosmological time is invoked (in this case out to z~4). The trends could be (partly) caused by this: the M/L of z~4 galaxies can be very different with respect to the M/L of z~0 galaxies (say at fixed mass, morphology, velocity dispersion, etc).
–
>> We agree with the reviewer that the M/L ratio of z~4 galaxies may be different that of z~0 galaxies. The trends reported in our study rely on stellar masses derived from abundance matching, which is calibrated for central halos (i.e. isolated galaxies; Moster+2023). The M/L ratio does not factor into the analysis of the simulation data and cannot explain our reported trends.  We agree that observational studies comparing galaxies selected from stellar mass cuts at high and low z galaxies should account for such differences in their errors.  We stress that the goal of this study is to identify whether any physical differences should be expected in the pair fractions of low and high mass galaxies in an ideal LCDM theoretical study.
–

2) On figure 3, for instance, the decreasing trend consistently found in low mass pairs (minor and major), could be produced by the selection of isolated pairs. Statistically, there are far more low mass galaxies in any cosmological volume, but there is also the assembly of lower mass halos into more massive structures, so the decreasing trend towards low z may just be caused by the details of the selection that progressively eliminates more pairs as they will be found in groups. This should be clarified, as an observational comparison will not only need an assumption of virial radius (as mentioned above) but also the selection of isolated pairs as in the adopted methodology.
–
>>We thank the reviewer for this comment. We have added additional text to make it clear that our reported trends are unique to our selection criteria, and may well be different for non-isolated low mass halos.

The primary goal for this study is to set the theoretical foundation for isolated pair fraction studies that seek to understand/quantify the differences between low mass and high mass pairs. Specifically, our goal is to identify if any differences in pair fractions are expected to exist in LCDM theory - the idea pointed out by the referee, that lower mass halos may assemble into more massive structures, would indeed be a prediction from LCDM theory that a such a study of pair fractions could in fact illustrate. We have added a section 5.4 to make this point and thank the referee for this comment.

Because  our selection methodology identifies halo pairs independently at each snapshot, it is true that some low mass galaxies may not be identified in our sample at one redshift but do enter the sample at another. The exact physical processes responsible for the trends we identify in this paper require tracking the individual halos across cosmic time and will be addressed in our next study.
–

I would like to see a better explanation as to why abundance matching(AM) is used instead of directly taking the stellar mass of the galaxies in TNG. The authors give a not too convincing explanation in 2.3, and the worry is that the predictions will inherit potential systematics from AM.
–
>> We thank the referee for raising this issue and have adjusted section 2.3 accordingly. The intention behind using abundance matching is threefold:
First, abundance matching allows us a prescriptive way to perform equivalent analyses for fair comparison in both the TNG Hydro and TNG Dark simulations (mentioned in section 2.3 paragraph 2).
Second, abundance matching allows us to remain independent of the specific subgrid physics that is implemented in the TNG Hydro simulation (mentioned in section 2.3 paragraph 3). Different hydrodynamical simulations use alternative subgrid physics, therefore it is likely that applying our analysis to another simulation suite using simulation stellar masses would yield different results. The abundance matching technique voids such uncertainties.
Third, abundance matching permits many realizations of stellar masses to account for the observed spread of stellar masses at a fixed halo mass, or uncertainties in the M/L ratio in the determination of stellar mass. Otherwise, we would only be able to perform this analysis for a singular given realization from the simulation. 	
We have improved some of the language in this section to make it more clear that there are a variety of reasons to use abundance matching, and added a mention of the third point above more explicitly in section 2.3 paragraph 4. Fortunately, the abundance matching method of Moster+2013 already includes ~1 dex spread in the stellar mass associated with a halo of mass ~1e11Msun. The uncertainty in the AM relationship is built into our analysis as we sample the abundance matching relation many times within this error space.
–

The authors should include a more extended comparison of their work with observationally motivated studies that assessed the growth of galaxy mass in groups of close pairs (see, e.g., Ferreras et al. 2013, Man et al. 2016, Conselice et al. 2022). Section 5.2 discusses some recent work on pair fractions, such as Besla et al. 2018, that compares low mass close pairs in SDSS with Illustris. Note the notorious low completeness at very close separation of SDSS, which would make the proposed separations presented here very challenging for actual survey data. The Snyder et al. (2017) reference focuses on more massive galaxies in the Illustris simulation, and compares with Man et al. (2016). No figure in the manuscript shows any results from observational constraints. The crux of the methodology proposed here is how one can implement a separation selection based on the virial radius in observational data. I think the connection with observations is fundamental if this paper is to make a substantial step forward.
–
>> We thank the reviewer for this comment. The intention of this paper is to show systematically that: 1) pair fractions evolve as a function of redshift; and 2) the behavior of low mass pairs and high mass pairs differs in a theoretical setting. We have edited text in the discussion section to make this clearer, and to highlight that this work is not a mock survey study. As pointed out by the referee, our pair selection choices differ markedly from that utilized by most observational studies.  As such, we do not attempt to compare our results with those of observational pair fraction studies. We have also adjusted the title of this paper to better reflect our intention.

Instead, we do compare with other simulation based pair fraction studies (some of which have their own comparisons to observational data) to ensure that our results are consistent. While these papers all use mock catalogs to compute pair fractions, they use much of the same methodology for selection that we do.

However, we do want to emphasize that, while our methodology may be challenging to adapt observationally, we have identified important selection considerations for performing observational pair fraction studies of different galaxy masses at different redshifts. The observational community should be made aware of these issues if comparisons to cosmological simulations is desired.  
–

Moreover, regarding the implementation with real data, note, for instance, that the quoted minimum separation (10 kpc) in page 6, col 1, line 399, would be at the resolution limit in most ground-based surveys at intermediate redshift. I think the actual apparent separation criterion should be led by the observational limits, and not the resolution limits of the simulation.
–
>> The minimum separation of 10 kpc is necessary to avoid incompleteness issues in the simulations. 10 kpc corresponds to a few times the simulation softening length.  It is not in the scope of this present work to include the effect of observational limits on the recovery of the pair fractions.
–

Figure 3: The fiducial separation to define a pair should be quoted in the caption, as the next figure extends on this choice of separation.
–
>> We thank the reviewer for this comment, and have added this in the caption of Figure 3. 
–

Overall, while this is a matter of taste, I would remove the brief paragraphs introduced in each section that describe what will be done in that section. I find it acceptable to do this type of brief description at the end of the introduction, regarding the whole paper. Doing this in each section seems like a page filler, and rather kills the flow of the text.
–
>> We thank the reviewer for this comment, and have decided to leave the introductory paragraphs of each section for ease of navigation for the reader.
–

In section 3, page 6, col 2, line 450, the number of pairs would be better understood if quoted as a fraction, or at least emphasize that the sample is defined within a fixed comoving volume at those two redshifts.
–
>> We thank the reviewer for this comment. We have added a line in the text to specify that this sample is defined with a fixed comoving volume in section 3.
–

### 2024-06-06 apj_sub/resubmission-Dec2023/pears.tex
deploy: 25aee7d523218253c42225dd158be0e25da52704

\documentclass[twocolumn]{aastex631}

@@

\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}

@@

%% This is the end of the preamble.

\begin{document}

\title{
  % Pair fractions of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
  % low mass and high mass galaxy pairs evolve differently as a function of redshift
  A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
  % A physically motivated framework for measuring galaxy pair fractions across cosmic time
   % for measuring galaxy pair fractions across cosmic time
   % measuring or recovering?
  }
% Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation

@@

\author[0000-0002-1871-4154]{Dave Patton}
\affiliation{\afftrent}

@@

\begin{abstract} 
Low mass galaxy pair fractions are under-studied across cosmic time. 
In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts. 
We use the Illustris TNG100 simulation to identify pairs between $z=0-4.2$ that are physically associated, free from contamination owing to projection effects.
We construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, using abundance matching to assign stellar masses. 
The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$).
Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context,

%  changed by rec. of garreth
and show that isolated analogs of LMC--SMC-mass pairs, as well as MW--LMC-mass pairs with low separation ($<50\kpc$), are $2-3\times$ more common at $z\gtrsim2-3$.
%quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.

\end{abstract}

@@

    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.
    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.

@@

@@

    This paper is structured as follows. 
    In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
    In Section~\ref{sec:pairprops}, we provide an overview of the properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
    We present the time-evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
    In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs. 
    Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.

@@

    We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
    This allows us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
    As such, we must ensure that our target subhalos are sufficiently isolated.  
    We do this by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.

@@

    First, at each snapshot, we apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated. The corresponding virial radius in TNG100 is given by \texttt{Group\_R\_TopHat200}.} in the TNG100 group catalogs. 
    We define the group mass range for low mass and high mass groups as: 
    \begin{align*}
        \mbox{\textbf{low mass:}}&\,\rm M_{G} = 8\times 10^{10}- 5\times 10^{11}\,\Msun \\ 
        \mbox{\textbf{high mass:}}&\, \rm M_{G}=10^{12}- 6.5\times10^{12}\,\Msun.
    \end{align*}
    The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
    % Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.

    By requiring that the FoF group virial mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs. 
    For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair.

@@

    Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}. 
    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects. 
    Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way. 
    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.

    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.

    Because the abundance matching prescription is calibrated for centrals of FoF groups, we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
    Thus, $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.

    Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{\mathrm{peak}}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.

    Using $z_{\mathrm{snap}}$ means that we account for changes in the stellar mass of both the primary and secondary halo, even after the secondary has entered the primary's halo. 
    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{Geha2013}, which found that dwarfs $>1.5\,\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.

    We then calculate the stellar mass for a given subhalo by Gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
    We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw from the SMHM distribution for each subhalo. 
    For each snapshot, we repeat this process 1000 times to generate 1000 realizations of stellar masses for the \subcat.
    The resulting catalog is called the \starcat, and consists of the set of all subhalos from the \subcat, as well as the 1000 stellar mass realizations. 
    Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties. In addition, our pair stellar mass selection criteria will result in different collections of subhalos being selected in each realization, since the stellar masses van

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Pair selection section %
    \subsection{Pair selection}\label{sec:methods-pairs}
    Starting from the \starcat, here we outline the pair matching process through which we generate the \paircat. 
    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a ``primary" and a ``secondary", where primaries are the more massive of the pair by stellar mass.

>>>>

\documentclass[linenumbers,twocolumn]{aastex631}

@@

\newcommand{\add}[1]{\textcolor{red}{\textbf{#1}}}

@@

%% This is the end of the preamble.
\begin{document}

\title{
  % Pair fractions of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
  % low mass and high mass galaxy pairs evolve differently as a function of redshift
  %A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
  \add{A physically motivated framework to compare pair fractions\\ of isolated low and high mass galaxies across cosmic time }

   % for measuring galaxy pair fractions across cosmic time
   % measuring or recovering?
  }
% Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation

@@

\author[0000-0002-3204-1742]{Nitya Kallivayalil}
\affiliation{\affuva}

\author[0000-0002-1871-4154]{David Patton}
\affiliation{\afftrent}

@@

\begin{abstract} 
    Low mass galaxy pair fractions are under-studied, 
    \add{and it is unclear whether low mass pair fractions evolve in the same way as more massive systems over cosmic time.} 
    \add{In the era of JWST, Roman, and Rubin, selecting galaxy pairs in a self-consistent way will be critical to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.}
    \add{Utilizing the Illustris TNG100 simulation, we create a sample of physically associated low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) pairs between $z=0-4.2$.}
    The low mass pair fraction increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than high mass pairs, consistent with findings for cosmological merger rates. 
    \add{We show that separation limits that vary with the mass and redshift of the system, such as scaling by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$), are critical for recovering pair fraction differences between low mass and high mass systems.}
    \add{Alternatively, static physical separation limits applied equivalently to all galaxy pairs do not recover the differences between low and high mass pair fractions, even up to separations of $300\,\kpc$.}
    Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context, showing that isolated analogs of LMC--SMC-mass pairs, and low separation ($<50\kpc$) MW--LMC-mass pairs, are $2-3\times$ more common at $z\gtrsim2-3$.

    % old abstract:
    % Low mass galaxy pair fractions are under-studied across cosmic time. 
    % In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts. We use the Illustris TNG100 simulation to identify physically associated pairs between $z=0-4.2$. 
    % Our sample includes low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, with stellar masses from abundance matching. 
    % The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
    % At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than high mass pairs, consistent with findings for cosmological merger rates. 
    % Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
    % Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
    % Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$). 
    % Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context, showing that isolated analogs of LMC--SMC-mass pairs, and low separation ($<50\kpc$) MW--LMC-mass pairs, are $2-3\times$ more common at $z\gtrsim2-3$.
\end{abstract}

@@

@@

    Typically, 
    \add{pair fraction studies via simulations and observations}
    apply physical projected separation cuts that are constant over time and do not vary with the mass of the target system. 
    \add{In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and show that a time and mass evolving separation cut is necessary to permit equitable pair fraction comparisons across different mass regimes.} 
    \add{Although implementing alternative selection criteria in future observational pair fraction studies may not always be strictly necessary, we recommend that pair selection criteria be reevaluated for observational studies that seek to compare pair fractions as a function of mass or redshift.}
    % In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
    % To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.

@@

    This paper is structured as follows. 
    In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
    In Section~\ref{sec:pairprops}, we provide an overview of the properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
    We present the time-evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
    \add{In Section~\ref{sec:discussion}, we give context to our results by drawing comparisons to Local Group pairs and other Illustris-based pair fraction studies, and discuss implications for observational campaigns.}
        % In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs. 
    Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.

@@

    % reworded for clarity
    % We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. This allows us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}. As such, we must ensure that our target subhalos are sufficiently isolated. We do this by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.
    \add{To assess whether the pair fractions of low mass and high mass pairs evolve in fundamentally different ways as a function of redshift, rather than as a product of their environmental conditions, we will focus on galaxy pairs in low density environments only\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
    As such, we ensure that our target subhalos are sufficiently isolated by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.}

@@

    At each snapshot, we first apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated. The corresponding virial radius in TNG100 is given by \texttt{Group\_R\_TopHat200}.} in the TNG100 group catalogs. 
    We define the group mass range for low mass and high mass groups as: 
    \begin{align*}
        \mbox{\textbf{low mass:}}&\,\rm M_{G} = 8\times 10^{10}- 5\times 10^{11}\,\Msun \\ 
        \mbox{\textbf{high mass:}}&\, \rm M_{G}=10^{12}- 6.5\times10^{12}\,\Msun.
    \end{align*}
    The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.

    By requiring that the FoF group virial mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs. 
    For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
    % reworded for clarity
    %We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair. 
    \add{Over 99\% of subhalos selected from FoF groups in these mass limits are not within $1.5\,\Mpc$ of a more massive perturber at $z=0$.}

@@

    \add{First, and primarily, utilizing an abundance matching prescription enables the direct comparison of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical and prescriptive way. 
    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.}

    \add{Second, while the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
    In particular, we would like to avoid a dependence between our results and the particular subgrid physics model implemented in \tng{}.}

    \add{Third, abundance matching allows us to account for the observed spread in the SMHM relationship, as we can sample the relation many times to get a distribution of stellar masses for each subhalo in the simulation. Otherwise, we would only be able to perform this analysis once given the set of stellar masses from the simulation. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}. }

    %Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
    %This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}. 
    %While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects. 
    %Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way. 
    %We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.

    We use the abundance matching relationship presented in~\citet{Moster2013}.
    %which provides an analytic prescription to assign stellar masses to dark matter halos. 
    \add{The SMHM relationship therein provides an analytic prescription to assign stellar masses to dark matter halos as a function of subhalo mass and redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
    We were careful to choose the input subhalo mass and redshift that would assign the most accurate stellar masses to each halo given their individual histories.}
    %The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
    %incomplete thought: The subhalo mass and redshift that are used to calculate the stellar mass impacts the stellar mass that is assigned to a given halo. For example, a satellite subhalo may have some of its associated dark matter stripped away by its host, while the stellar mass remains roughly the same throughout the loss of a significant portion of

    The abundance matching prescription is calibrated for centrals of FoF groups, thus we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
    Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{\mathrm{peak}}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.

    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
    Using $z_{\mathrm{snap}}$ means that we account for changes in the stellar mass of both the primary and secondary halo, even after the secondary has entered the primary's halo. 
    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{Geha2013}, which found that dwarfs $>1.5\,\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}. 
    Thus, our abundance matching prescription is of the form $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.

    We calculate the stellar mass for a given subhalo by Gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
    %We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw from the SMHM distribution for each subhalo. 
    \add{We generate a single stellar mass ``realization" using an independent draw from the SMHM distribution to calculate a stellar mass for each subhalo of the full \subcat.}
    For each snapshot, we repeat this process 1000 times to generate 1000 separate realizations of assigned stellar masses for the \subcat.
    The resulting catalog is called the \starcat, and consists of the set of all subhalos from the \subcat, as well as the 1000 stellar mass realizations. 
    Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Pair selection section %
    \subsection{Pair selection}\label{sec:methods-pairs}
    Starting from the \starcat, we outline the pair matching process used to generate the \paircat below. 
    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a ``primary" and a ``secondary", where primaries are the more massive of the pair by stellar mass.
